Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-04-02 doc/PRF2022/Reviews/ResponseToReviewer2.tex

  We point out though, that because the wave vector $\mathbf{k}$ is inversely
  proportional to the characteristic phase-sample size,
  fluctuation will be large provided $L_x$ or $L_y$ is sufficiently large,
  as in the case of micron-sized vesicles.
\end{itemize}

\noindent
\comment{2) The shear rates studied are below nanoseconds$^{-1}$. What is the relevance of
such small shear rates in real (biological) systems? Furthermore, in presence of
noise, I would expect that the JP diffusive timescale is much smaller then the
shear flow time scale, and hence effectively the associated Peclet number, i.e.
importance of flow compared to noise, is negligible in this system?

Before I can recommend publication, the authors should clarify these points, in
particular justify why noise can be neglected, and why such small shear rates
are relevant.}

\begin{itemize}
\item {\bf Response:}
  In the beginning  of the new Section V ``Results and Discussion'' (page 12),
  we now derive the range of shear rates 
  based on the capillary number $\mathrm{Ca}$.  The derivation shows that shear forces dominate
  interfacial forces when $\dot \gamma$ exceeds
  10$^{-2}$ ns $^{-1} = 10^6$ s$^{-1}$.  Following the derivation,
  we include references to molecular dynamics simulations that also
  consider nm system-sizes like ours and use the same shear rates,
  along with references to
  larger experimental systems were shear rates are more moderate,
  on the order of $10^3$ s$^{-1}$.  We end by calculating the
  P\'eclet number $\mathrm{Pe} = 60$, showing that
  noise is negligible compared to advection in our system.

  Although the range of simulation shear rates is unchanged in our
  revision, we thank the Reviewer for pointing these details out
  as their comment has clarified
  two important points: how we chose the range of shear
  rates that we did and how neglecting noise and
  thermal fluctuation can be justified in our system.

### 2023-04-25 doc/PRF2022/PRF_main.tex
Peter updated files

%\usepackage{showkeys}
\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\usepackage{color,soul}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$.
  The three rightmost panels plots show $g(\xx)$ and
  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
  for an isolated particle.}
\end{caption}
\end{figure}

@@

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure1and2.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
%  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
%  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows the $t = 0$, $N_b = 198$ particle configuration with
  random orientation and initially confined to a box. Panels (b), (d),
  (e) show bilayer, multilamellar, and striated phases composed of
  amphiphilic (Type I), asymmetric hydrophobe (Type II), and polar (Type
  III) JP, respectively. Panels (c) and (f) plot the free
  energies~\eqref{eq:free_energy} and alignment order
  parameter~\eqref{eq:S2} with respect to $t$. The open markers in panel
  (c) are for $N_b = 60$ and the solid markers are for $N_b = 198$ but
  normalized by $60/198$, showing that the energy approximately scales
  with the number of particles. Alignment in the striated phase is
  particle-number dependent; triangle markers, panel (f).}
\end{caption}
\end{figure}

@@

See Section~\ref{sec:movie_description} in the [Supplementary Material]
for movies showing the transition of 60 JPs that are initialized
randomly (inset of Figure~\ref{fig:relax}(a)) to the steady state
configurations (inset of Figures~\ref{fig:relax}(b), (d), and (e)).

@@

%%%%%%%
{\color{red}
\section{Results and Discussion}}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
{\color{red}
  \begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
  \end{equation}
  }
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $\pi \lambda \times \pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

@@

Figure~\ref{fig:s2esummary}(e)--(l) show the typical streamlines for JP
phases in background flow. Although the plots only show the region near
the JPs, the fluid velocity $\uu$ and order parameter $u$ are accounted
for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the rigid
boundary condition at every JP-fluid interface i.e., the particles
interact with the local flow field and are not merely carried by
background flow. See Section~\ref{sec:movie_description} in the
[Supplementary Material] for movies showing the dynamics of the JP
suspensions in Figure~\ref{fig:s2esummary}.

Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
Material] contain the fully-resolved time courses for the free energy
$F$, alignment order $S_2$, and strain $E$. The eight setups correspond
to the four JP phases---bilayer, vesicle BL, multilamellar, and
striated---and two background flows---shear and TG, and the data are
plotted with the same vertical and horizontal axes to facilitate
comparisons between simulation setups. Each setup considers a range of
shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses in
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
Material] contain significant oscillations due to the particle-based
formulation and tumbling inherent to the background flows. To extract
meaningful data, we further post-process the $F$, $S_2$, $E$ curves by
taking their time average over the interval $t \in [0, T]$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{FSummary.pdf}
\end{center}
\caption{\label{fig:fsummary}
  The change of average free energy versus shear rates for shear flow
  and TG flow simulation results are plotted in panels (a)-(b). Panel
  (c) contains quadratic fits to the change in free energy as a function
  of displacement in interparticle distance from equilibrium.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary} Rheology of Type I, II, and III
  phases. Panel (a) shows that bilayer phases behave as a Newtonian
  fluid. Panel (b) provides that the multilamellar phase shows a near
  shear thinning behaviour. A pseudoplastic behaviour of deformation in
  striated phases is shown in panel (c).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely constant
strains maintained by an external force provided by background flow.
Now we consider dynamic material properties. Specifically, we look at
the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that the shear flow
$\uu_{\infty}^{\text{sh}}$ simulations correspond to a complex fluid
within a drag plate rheometer where the shear stress is set by $\mu
\dot\gamma$ and the observed, sample shear rate is $\dot E$. The
definitions carry over to the TG flow case directly. Also, as a
practical consideration, the rotation of non-isotropic JP phases in the
background flow leads to oscillation in the strain time courses making
systematic fitting challenging (see [Supplementary Material]
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral
in~\eqref{eq:strainrate} averages out these oscillations and gives
physically meaningful values.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $\lambda= 1,2,3,4$,
  respectively. In panel (f),
  inset, the relative enclosed area $A/A_0$
  for the four cases in panels (b)--(e) decays to a steady state.
  The steady-state $A_{\infty}/A_0$ relative area is non-monotonic
  in $\lambda$.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$~ns$^{-1}$
by analyzing the capillary number of the JP phases. With this range,
there is a critical shear rate $\dot \gamma_*$ for the vesicle BL and
striated phases where shear stresses exceeded elastic stresses, leading
to rupture. The multilamellar phase did not rupture. By varying model
parameters, we perform a dimensional analysis on $\dot \gamma_*$.
Focusing on Type III JPs in shear flow, $\dot \gamma_* = 0.14$ ns$^{-1}$
for the basic model parameters (see
Section~\ref{sec:tunable_hydrophobicity}). Increasing and decreasing the
tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear rate (denoted $\Delta \dot
\gamma_*/\dot \gamma_*$). This suggests that the critical shear rate
scales linearly with the tension parameters. Conversely, increasing
(resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$ by up
to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative decrease (resp.~increase) in the critical shear rate. This
points to an inverse-quadratic scaling in length.
Figure~\ref{fig:PramChange}(a) summarizes the findings and suggests the
scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow. Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary movie). Our previous
work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
K_{\text{I}} \gamma c^2/(\rho L^2)$ for a vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
Figure~\ref{fig:PramChange}(e).
%As shown in the Supplementary Material Movie S6,
These JP vesicles fluctuate and deform around a steady shape of an
octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm). See
Section~\ref{sec:movie_description} in the [Supplementary Material] for
a movie showing the dynamics of the JP vesicle for the four different
values of $\lambda$ in Figure~\ref{fig:PramChange}(b)--(e).

@@

\input{Supplementary}

>>>>

%\usepackage{showkeys}
%\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\usepackage{color,soul}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figure1.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$.
  The three rightmost panels plots show $g(\xx)$ and
  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
  for an isolated particle.}
\end{caption}
\end{figure}

@@

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figure2.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows the $t = 0$, $N_b = 198$ particle configuration with
  random orientation and initially confined to a box. Panels (b), (d),
  (e) show bilayer, multilamellar, and striated phases composed of
  amphiphilic (Type I), asymmetric hydrophobe (Type II), and polar (Type
  III) JP, respectively. Panels (c) and (f) plot the free
  energies~\eqref{eq:free_energy} and alignment order
  parameter~\eqref{eq:S2} with respect to $t$. The open markers in panel
  (c) are for $N_b = 60$ and the solid markers are for $N_b = 198$ but
  normalized by $60/198$, showing that the energy approximately scales
  with the number of particles. Alignment in the striated phase is
  particle-number dependent; triangle markers, panel (f).}
\end{caption}
\end{figure}

@@

See Section~\ref{sec:movie_description} in the Supplementary Material
for movies showing the transition of 60 JPs that are initialized
randomly (inset of Figure~\ref{fig:relax}(a)) to the steady state
configurations (inset of Figures~\ref{fig:relax}(b), (d), and (e))~\cite{supp}.

@@

%%%%%%%
{\color{red}
\section{Results and Discussion}}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{Figure3.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
{\color{red}
  \begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
  \end{equation}
  }
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $\pi \lambda \times \pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

@@

Figure~\ref{fig:s2esummary}(e)--(l) show the typical streamlines for JP
phases in background flow. Although the plots only show the region near
the JPs, the fluid velocity $\uu$ and order parameter $u$ are accounted
for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the rigid
boundary condition at every JP-fluid interface i.e., the particles
interact with the local flow field and are not merely carried by
background flow. See Section~\ref{sec:movie_description} in the
Supplementary Material for movies showing the dynamics of the JP
suspensions in Figure~\ref{fig:s2esummary}~\cite{supp}.

Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the Supplementary
Material contain the fully-resolved time courses for the free energy
$F$, alignment order $S_2$, and strain $E$~\cite{supp}. The eight setups correspond
to the four JP phases---bilayer, vesicle BL, multilamellar, and
striated---and two background flows---shear and TG, and the data are
plotted with the same vertical and horizontal axes to facilitate
comparisons between simulation setups. Each setup considers a range of
shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses in
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the Supplementary
Material contain significant oscillations due to the particle-based
formulation and tumbling inherent to the background flows~\cite{supp}. To extract
meaningful data, we further post-process the $F$, $S_2$, $E$ curves by
taking their time average over the interval $t \in [0, T]$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{Figure4.pdf}
\end{center}
\caption{\label{fig:fsummary}
  The change of average free energy versus shear rates for shear flow
  and TG flow simulation results are plotted in panels (a)-(b). Panel
  (c) contains quadratic fits to the change in free energy as a function
  of displacement in interparticle distance from equilibrium.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{Figure5.pdf}
\end{center}
\caption{\label{fig:rheologysummary} Rheology of Type I, II, and III
  phases. Panel (a) shows that bilayer phases behave as a Newtonian
  fluid. Panel (b) provides that the multilamellar phase shows a near
  shear thinning behaviour. A pseudoplastic behaviour of deformation in
  striated phases is shown in panel (c).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely constant
strains maintained by an external force provided by background flow.
Now we consider dynamic material properties. Specifically, we look at
the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that the shear flow
$\uu_{\infty}^{\text{sh}}$ simulations correspond to a complex fluid
within a drag plate rheometer where the shear stress is set by $\mu
\dot\gamma$ and the observed, sample shear rate is $\dot E$. The
definitions carry over to the TG flow case directly. Also, as a
practical consideration, the rotation of non-isotropic JP phases in the
background flow leads to oscillation in the strain time courses making
systematic fitting challenging (see Supplementary Material
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}~\cite{supp}). The integral
in~\eqref{eq:strainrate} averages out these oscillations and gives
physically meaningful values.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{Figure6.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $\lambda= 1,2,3,4$,
  respectively. In panel (f),
  inset, the relative enclosed area $A/A_0$
  for the four cases in panels (b)--(e) decays to a steady state.
  The steady-state $A_{\infty}/A_0$ relative area is non-monotonic
  in $\lambda$.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$~ns$^{-1}$
by analyzing the capillary number of the JP phases. With this range,
there is a critical shear rate $\dot \gamma_*$ for the vesicle BL and
striated phases where shear stresses exceeded elastic stresses, leading
to rupture. The multilamellar phase did not rupture. By varying model
parameters, we perform a dimensional analysis on $\dot \gamma_*$.
Focusing on Type III JPs in shear flow, $\dot \gamma_* = 0.14$ ns$^{-1}$
for the basic model parameters (see
Section~\ref{sec:tunable_hydrophobicity}). Increasing and decreasing the
tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear rate (denoted $\Delta \dot
\gamma_*/\dot \gamma_*$). This suggests that the critical shear rate
scales linearly with the tension parameters. Conversely, increasing
(resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$ by up
to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative decrease (resp.~increase) in the critical shear rate. This
points to an inverse-quadratic scaling in length.
Figure~\ref{fig:PramChange}(a) summarizes the findings and suggests the
scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow. Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary movie~\cite{supp}). Our previous
work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
K_{\text{I}} \gamma c^2/(\rho L^2)$ for a vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
Figure~\ref{fig:PramChange}(e).
%As shown in the Supplementary Material Movie S6,
These JP vesicles fluctuate and deform around a steady shape of an
octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm). See
Section~\ref{sec:movie_description} in the Supplementary Material for
a movie showing the dynamics of the JP vesicle for the four different
values of $\lambda$ in Figure~\ref{fig:PramChange}(b)--(e)~\cite{supp}.

@@

%\input{Supplementary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty}

\newpage
{\Large \bf

  \noindent Supplementary Material\\

  \noindent 
 Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows}\\

\noindent 
Szu-Pei Fu$^{1,*},$ 
Rolf Ryham$^{2},$ 
Bryan Quaife$^{3}$ and Y.-N. Young$^{4},$
\\

\noindent
$^{1}$Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA

\noindent
$^{2}$Department of Mathematics, Fordham University, Bronx, NY, USA

\noindent
$^{3}$Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA

\noindent
$^{4}$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, NJ 07102 USA
\\

\noindent $^*$Corresponding author. Address: Department of Mathematics, Trinity College, 
300 Summit Street, Hartford, CT 06106. email: \text{peter.fu@trincoll.edu}

\setcounter{page}{1}

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}

\setcounter{section}{0}
\renewcommand{\thesection}{S\arabic{section}}

%-----ellipse repulsion--------------------

%\Phi_{\mathrm{rep}}

\section{Movie Descriptions}
\label{sec:movie_description}
We consider suspensions of JPs of radius 1.25~nm. The time step size for
all simulations is $\Delta t = 0.2$~ns. The colors of the JPs are as
follows: for Type I and Vesicles, red is hydrophobic ($\max g > 0$) and
blue is hydrophilic ($\min g = 0$); for Type II, red is more hydrophobic
($\max g >0$) than blue ($\min g > 0$); for Type III, red is positively
charged ($\max g > 0$) and blue is negatively charged ($\min g < 0$).
%\mbox{} \\

\noindent
{\bf Relaxation}: The relaxation of 60 circular JPs that are initialized
with random locations and orientations. The JPs self-assemble into
unilamellar (Type I), multilamellar (Type II), and striated (Type III)
configurations. The final configurations are used as initial conditions
for the simulations that include a background flow.

%There are 60 circular particles with radius 1.25~nm that are initially
%confined in a square box. The simulation results show the relaxation
%with each of the three boundary conditions. The time step of all
%simulations is $\Delta t=0.2$. The color on the boundary from blue to
%red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
%adopted in simulations with hydrodynamic flows. \\

\noindent
{\bf Structures in a Weak Shear Flow}:
The relaxed configurations of the 60 JPs are subjected to a weak shear
flow. The shear rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for the Vesicle,
Type I, and Type II configurations, and $\dot{\gamma} = 0.1$~ns$^{-1}$
for the Type III configuration. The vesicle undergoes tank-treading and
the bilayer increases its orientational order. The multilamellar
configuration resembles a rigid body motion, and the striated
configuration has an even stronger resemblance to a rigid body motion.
No ruptures occur in these examples. The frame rate for the movie of 
Type I configuration is twice as much ones used in movies of other configurations.

%We adopt the relaxed configurations and place the JP structures in the
%shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
%0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
%bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the multi-lamellar, and
%$\dot\gamma = 0.1$ ns$^{-1}$ for the striated configurations. The
%vesicle case undergoes tank-treading whereas the initially disordered
%BC (i) case increases orientational order. The multilamellar assemply
%behaves as a rigid body, and the striated configuration moreso. No
%ruptures occur. \\

\noindent
{\bf Structures in a Weak Taylor-Green Flow}:
The relaxed configurations of the 60 JPs are subjected to a weak
Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for
the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
0.1$~ns$^{-1}$ for the Type III configuration. The vesicle stays intact,
whereas the bilayer is pulled apart into different TG cells. Like in the
weak shear flow example, the multilamellar and striated configurations
behave as rigid bodies.

%For the choices of the flow strength, we pick: $\dot\gamma = 0.05$
%ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
%disordered bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the
%multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$ for the striated
%configurations. The vesicle stays inact, whereas the dissordered
%bilayer is pulled apart. Like in Supplementary Movie S2, the striated
%assembly is basically rigid. \\

%We adopt the relaxed configurations and place the JP structures in the
%Taylor-Green flow at low flow rates. For the choices of the flow
%strength, we pick: $\dot\gamma = 0.05$ ns$^{-1}$ for the vesicle,
%$\dot\gamma = 0.05$ ns$^{-1}$ for the disordered bilayer, $\dot\gamma =
%0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$
%ns$^{-1}$ for the striated configurations. The vesicle stays inact,
%whereas the dissordered bilayer is pulled apart. Like in Supplementary
%Movie S2, the striated assembly is basically rigid. \\

\noindent
{\bf Structures in a Strong Shear Flow}:
The relaxed configurations of the 60 JPs are subjected to a strong shear
flow. The shear rate is $\dot{\gamma} = 0.075$~ns$^{-1}$ for the Vesicle
configuration, $\dot{\gamma} = 0.1$~ns$^{-1}$ for the Type I
configuration, and $\dot{\gamma} = 0.15$~ns$^{-1}$ for the Type II and
Type III configurations. In all cases, the structure is ruptured by the
flow. The frames are stabilized by moving with the center of mass of all
the JPs.

%We adopt the relaxed configurations and place the JP structures in the
%shear flow at a higher shear rate. For the choices of the shear rate, we
%pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$
%for the bilayer, $\dot\gamma = 0.15$ ns$^{-1}$ for the multi-lamellar,
%and $\dot\gamma = 0.15$ ns$^{-1}$ for the striated configurations. The
%time step of all simulations is $\Delta t=0.2$ ns$^{-1}$. In this movie,
%some clear structural ruptures occur in each case. In order to observe
%the structure behaviors at later time, we stabilize the frame by
%tracking the center of mass position of all JP. \\

\noindent
{\bf Structures in a Strong Taylor-Green Flow}:
The relaxed configurations of the 60 JPs are subjected to a strong
Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.1$~ns$^{-1}$ for
the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
0.15$~ns$^{-1}$ for the Type III configuration. In all cases, the
structure is ruptured by the flow and there is a significant reduction
in the orientation order. While the Vesicle Type I configurations are
broken into several pieces, the main body of the Type II and Type III
configurations are not pulled apart by the background flow.

%We adopt the relaxed configurations and place the JP structures in the
%Taylor-Green flow at higher flow rates. For the choices of the flow
%strength, we pick: $\dot\gamma = 0.1$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
%bilayer, $\dot\gamma = 0.1$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.15$ ns$^{-1}$ for the
%striated configurations. Clear structural ruptures occur in each case.
%In all cases, there is significant reduction in the orientational order
%of the assemblies. While the BC (i) cases are broken into several
%pieces, the main body of the BC (ii) and BC (iii) assemblies are not
%pulled apart by the background flow.\\

\noindent
%{\label{MovieS6}\bf JP Vesicle in a Taylor-Green Flow with Various
%$\lambda$ Values}: 
{\bf JP Vesicle in Various Taylor-Green Flows}: A circular vesicle
bilayer is placed in a Taylor-Green flow. The parameter $\lambda$
controls the TG cell size and the values are varied from 1~nm to 4~nm
while the flow rate is chosen so that $\lambda\dot\gamma=0.1$~nm/ns. The
parameter $\lambda$ determines the steady-state polygonal tank-treading
shape. The rotation direction is clockwise for $\lambda=1$~nm and
$\lambda=2$~nm, and counterclockwise for $\lambda=3$~nm and
$\lambda=4$~nm. Streamlines of the flow are included.

%A circular vesicle bilayer is placed in the Taylor-Green flow.  The
%parameter $\lambda$ controls the cell size and the values are varied
%from 1.0 nm to 4.0 nm while the flow rate $\lambda\dot\gamma=0.1$ is
%fixed. There is a rotation transition from clockwise ($\lambda=1$ nm and
%2 nm) to counterclockwise ($\lambda=3$ nm and 4 nm). Moreover, the
%resulting steady shapes of all cases are different polygons. We plot the
%streamlines in the background.\\
